---
title: "Bee Colonies"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(lubridate)
library(RColorBrewer)
```

## Bee colonies stressors

Let's read in the data first and look at the first few rows.
We will focus on the stressors of bee colonies

```{r}

stressor <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-11/stressor.csv')


```
The stressors being tracked are:

* Varroa mites
* Other pests/parasites
* Diseases
* Pesticides
* Other
* Unknown

We then do some data wrangling to get the dates in quarter format.

```{r wrangling}

stressor_with_quarters <- stressor %>% 
  mutate(date = case_when(
    months == 'January-March' ~ ymd(str_c(as.character(year),'01','01',sep = '-')),
    months == 'April-June' ~ ymd(str_c(as.character(year),'04','01',sep = '-')),
    months == 'July-September' ~ ymd(str_c(as.character(year),'07','01',sep = '-')),
    months == 'October-December' ~ ymd(str_c(as.character(year),'10','01',sep = '-'))
  ), quarter = lubridate::quarter(date,with_year = TRUE)) %>% 
  filter(state == 'United States')

```

The plot below shows the percentage of bee colonies affected by various stressors between 2015 - 2021.

```{r line plot}

stressor_with_quarters %>% ggplot(aes(x = quarter,y = stress_pct,color = stressor)) + 
  geom_line()+
  geom_vline(xintercept = 2019.2,linetype = 'dotted')+
  geom_curve(aes(x = 2019.4,y = 50,xend = 2019.2,yend = 55),size = 1,
             arrow = arrow(length = unit(0.03, "npc")))+
  geom_label(aes(x = 2019.4,y = 50,label = 'Missing data for\nQ2 2019.'),
             size = 3,color = 'red')+
  scale_color_brewer(type = 'qual')+
  labs(title = '% of Bee Colonies affected by stressors',
       subtitle = 'Colony can be affected by multiple stressors in a quarter.',
       caption = 'Source:USDA\n Graph:@kigtembu',
       y = '%',
       x = 'Year-Quarter')+
  theme_light()

```

There is missing data in Q2 2019. **Varroa mites** stand out as the biggest
stressor of bee colonies in the US.




