---
title: "Board Games"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)

library(tidyverse)
library(tidytuesdayR)
```



This week's tidytuesday dataset is about boardgames.More information can be found on the [tidy tuesday github page](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-25/readme.md)

```{r read-in_data,include=FALSE}

tuesdata <- tidytuesdayR::tt_load('2022-01-25')

```

```{r explore-data,echo=TRUE}

ratings <- tuesdata$ratings
details <- tuesdata$details

ratings %>% head()
details %>% head()


```

We can merge the two datasets `ratings` and `details` on `id`

```{r}

ratings_with_details <- ratings %>% inner_join(details,by = 'id')

```

Let's investigate whether there is a relationship between `Max no. of Players` and `average rating`.

```{r}
ratings_with_details %>%   
  select(average,maxplayers) %>% 
  ggplot(aes(maxplayers,average)) +
  geom_jitter()+
  theme_light()+
  labs(x = 'Max No. of Players allowed for the Board game',
       y = 'Average rating',
       title = 'Average rating vs Max No. of Players',
       caption = 'Source: Kaggle/Board Games geek\n Graph: @kigtembu')


```


There isn't a linear relationship between the Maximum number of players a board game  has and it's average rating.
