---
title: "Dog breeds"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)

library(tidyverse)
```

This week's(1/31) tidytuesday dataset is about dog breeds.More information can be found on the [tidy tuesday github page](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-25/readme.md)

```{r}
breed_rank_all <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-01/breed_rank.csv')

breed_rank_all %>% head()

```

The `breed_rank_all` dataset contains the popularity rankings of 165 breeds of dogs based on AKU registration characteristics from 2013 to 2020.
I take the top ten popular breeds as of 2020 and trace their rank over the years in their subset:

```{r path to top ten,echo=TRUE}

top_ten_breeds_reranked <- breed_rank_all %>% filter(`2020 Rank` <= 10) %>%
  #reranking step over the now 10 breeds
  mutate(across(where(is_numeric),row_number)) %>% 
  pivot_longer(where(is_numeric),names_to = 'year',values_to = 'ranking') %>% 
  #extract year from year column
  mutate(year = as.numeric(str_extract(year,"[0-9][0-9][0-9][0-9]")))

```

Let us now visualise this using a bump chart:

```{r plot,echo=TRUE}

top_ten_breeds_reranked %>% ggplot(aes(x = year,y = ranking,group = Breed))+
  geom_line(aes(color = Breed),size = 2)+
  geom_point(aes(color = Breed),size = 4)+
  scale_y_reverse(breaks = 1:nrow(top_ten_breeds_reranked))+
  scale_x_continuous(breaks = 2013:2020)+
  theme_light()+
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.ticks = element_blank()
  )+
  labs(
    x = 'Year',
    y = 'Ranking',
    title = 'Popularity of Dog Breeds in the US',
    caption = "Source: American Kennel Club\n Graph: @kigtembu"
  )
```

The french bulldog has had a meteoric rise in popularity over the last 8 years.